---
title: "TSF Task 1"
author: "Hrithik Agarwal"
date: "08/01/2021"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Prediction using supervised ML (Linear Regression)

Importing the required libraries

```{r, message= FALSE}
library(ggplot2)
library(GGally)
```

Importing and Reading Data

```{r}
d <- read.csv('https://raw.githubusercontent.com/AdiPersonalWorks/Random/master/student_scores%20-%20student_scores.csv')
```
```{r}
dim(d)
head(d)
```

### Cheacking for missing data

```{r}
sum(is.na(d))
```

Thus there is no Missing data.


## Plotting the Data

```{r}
ggplot(data = d,aes(y = Scores , x = Hours)) + geom_point()
```

From the graph we can observe that there is no future engineering reuired in the data.

## Correlation between the variables

```{r}
ggpairs(data = d , columns = 1:2)

```

The Correlation is **0.976** which is very significant.

## Training the model

```{r}
model <- lm(Scores ~ Hours, data = d)
```

### Summary of Model

```{r}
summary(model)
```

Since **Pr(>|t|)** << 1, it indicates that model is highly significant.

### Plotting the regression Line

```{r, message=FALSE}
ggplot(data = d,aes(y = Scores , x = Hours)) + geom_point()+geom_smooth(method = 'lm', color = 'red')

```

### Prediction on Our Dataset

```{r}
d2 <- data.frame(d$Hours)
names(d2)[1]<- 'Hours'
pred <- predict(model , )
pred <- as.numeric(pred)
pred
```

Comparing the Actual and Predicted Scores.

```{r}
actual <- as.numeric(d$Scores)
data.frame(actual,pred)
```

## Predicting for Hours = 9.25

```{r}
predict(model, data.frame(Hours = 9.25))

```

### Hence our model Predicts Score of **92.90985**




 


